%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%                 %%%%%%%%%%%%
%%%%%%%%%%%%%    EXERCISE 1   %%%%%%%%%%%%
%%%%%%%%%%%%%                 %%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{exercise}[]{
    Given six memory partitions of 300 KB, 600 KB, 350 KB, 200 KB, 750 KB,
    and 125 KB (in order), how would the first-fit, best-fit, and worst-fit
    algorithms place processes of size 115 KB, 500 KB, 358 KB, 200 KB, and
    375 KB (in order)?}
  \begin{solution}
    See Table \ref{1}, for every entry, the first number indicates the remaining space of partition and the second number indicates the original size of partition.
    \begin{table}[h]
        \centering
        \begin{tabular}{llllll}
            \hline
            & 115 KB     & 500 KB     & 358 KB     & 200 KB     & 375 KB    \\ \hline
  First-fit & 185/300 KB & 100/600 KB & 392/750 KB & 150/350 KB & 17/750 KB \\
  Best-fit  & 10/115KB   & 100/600 KB & 392/750 KB & 0/200 KB   & 17/750 KB \\
  Worst-fit & 635/750 KB & 135/750 KB & 242/600 KB & 150/350 KB & FAIL      \\ \hline
        \end{tabular}
        \caption{Exercise 1\label{1}}
        \end{table}
  \end{solution}
  \label{ex1}
\end{exercise}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%                 %%%%%%%%%%%%
%%%%%%%%%%%%%    EXERCISE 2   %%%%%%%%%%%%
%%%%%%%%%%%%%                 %%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{exercise}[]{Assuming a 1-KB page size, what are the page numbers and offsets for
    the following address references (provided as decimal numbers):
    \begin{enumerate}
        \item [a.] 3085
        \item [b.] 42095
        \item [c.] 215201
        \item [d.] 650000
        \item [e.] 2000001
    \end{enumerate}}
  \begin{solution} Assume that the addresses are given in terms of bytes. The results are given in decimal number.
    \begin{enumerate}
    \item [a.] Page number: 3, Offset: 13
    \item [b.] Page number: 41, Offset: 	111
    \item [c.] Page number: 210, Offset: 	161
    \item [d.] Page number: 634, Offset: 	784
    \item [e.] Page number: 1953, Offset: 	129
    \end{enumerate}
  \end{solution}
  \label{ex2}
\end{exercise}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%                 %%%%%%%%%%%%
%%%%%%%%%%%%%    EXERCISE 3   %%%%%%%%%%%%
%%%%%%%%%%%%%                 %%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{exercise}[]{Consider a logical address space of 256 pages with a 4-KB page size,
    mapped onto a physical memory of 64 frames.
    \begin{enumerate}
        \item [a.] How many bits are required in the logical address?
        \item [b.] How many bits are required in the physical address?
    \end{enumerate}}
  \begin{solution}
  \par{~}
  \begin{enumerate}
      \item Logical address requires $\log 256 + \log (4\cdot 1024) = 20$ bits.
      \item Physical address requires $\log 64 + \log (4\cdot 1024) = 18$ bits.
  \end{enumerate}
  \end{solution}
  \label{ex3}
\end{exercise}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%                 %%%%%%%%%%%%
%%%%%%%%%%%%%    EXERCISE 4   %%%%%%%%%%%%
%%%%%%%%%%%%%                 %%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{exercise}[]{Consider a computer system with a 32-bit logical address and 4-KB page
    size. The system supports up to 512 MB of physical memory. How many
    entries are there in each of the following?
    \begin{enumerate}
        \item [a.] A conventional, single-level page table
        \item [b.] An inverted page table
    \end{enumerate}}
  \begin{solution}
  \par{~}
  Number of pages is $2^{32 - \log(4\cdot 1024)} = 2^{20}$, and the number of frames is $512 MB / 4 KB = 2^{17}$.
  \begin{enumerate}
      \item Number of entries are equal to number of pages $2^{20}$
      \item Number of entries are equal to number of frames $2^{17}$.
  \end{enumerate}
  
  \end{solution}
  \label{ex4}
\end{exercise}